Flowchart of Current Algorithm

### 2008-10-13 docs/flowchart/paper.tex
Made a noteworthy notational change:
\newcommand{\uadvone}{\widetilde{\mathbf{U}}^{\mathrm{ADV},(1)}}
\newcommand{\uadvtwo}{\widetilde{\mathbf{U}}^{\mathrm{ADV},(2)}}

has now become

\newcommand{\uadvone}{\widetilde{\mathbf{U}}^{\mathrm{ADV},\star}}
\newcommand{\uadvtwo}{\widetilde{\mathbf{U}}^{\mathrm{ADV}}}

I really think this change has to be made because

the ^{n}, ^{(1)}, ^{(2)}, ^{n+1} notation refers to different points in the splitting scheme.

The ^{\star} vs ^{no star} notation has to do with the predictor/corrector algorithm.

The old definitions of \uadveone and \uadvtwo was mixi

\newcommand{\uadvone}{\widetilde{\mathbf{U}}^{\mathrm{ADV},(1)}}
\newcommand{\uadvtwo}{\widetilde{\mathbf{U}}^{\mathrm{ADV},(2)}}
\newcommand{\V}{\mathbf{V}}
\newcommand{\dt}{\Delta t}
\newcommand{\dr}{\Delta r}

@@

\item {\bf React Base}$[(\rho h)_0^{\inp}] \rightarrow [(\rho h)_0^{\outp}]$

@@

%--------------------------------------------------------------------------
% STEP 3
%--------------------------------------------------------------------------
\item[Step 3.] {\em React the full state through the first time interval of $\dt / 2.$}

\begin{enumerate}
\MarginPar{Need React Base}
\renewcommand{\theenumi}{{\bf \alph{enumi}}}

\item {\bf React State}$[\rho^n, (\rho h)^n, X_k^n, T^n, (\rho^n \Hext)]
                   \rightarrow$ $[ \rho^{(1)}, (\rho h)^{(1)}, X_k^{(1)}, T^{(1)},
                                  (\rho \omegadot_k)^{(1)}, (\rho \Hnuc)^{(1)} ].$

@@

\begin{enumerate}
\MarginPar{Need React Base}
\renewcommand{\theenumi}{{\bf \alph{enumi}}}

\item {\bf React State}$[ \rho^{(2),\star},(\rho h)^{(2),\star}, X_k^{(2),\star}, 
                             T^{(2),\star}, (\rho^{(2),\star} \Hext)] $\\
$\rightarrow [ \rho^{n+1,\star},(\rho h)^{n+1,\star}, X_k^{n+1,\star}, T^{n+1,\star}, 
              (\rho \omegadot_k)^{(2),\star}, (\rho \Hnuc)^{(2),\star} ].$

@@

\item Update the speces.  Here we do a difference approximation to
  eq.~\ref{eq:species}, neglecting the reaction terms.  The
  update consists of two steps:

@@

%--------------------------------------------------------------------------
% STEP 9
%--------------------------------------------------------------------------
\item[Step 9.] {\em React the full state through a second time interval of $\dt / 2.$}

\begin{enumerate}
\MarginPar{Need React Base}
\renewcommand{\theenumi}{{\bf \alph{enumi}}}

@@

>>>>

\newcommand{\uadvone}{\widetilde{\mathbf{U}}^{\mathrm{ADV},\star}}
\newcommand{\uadvtwo}{\widetilde{\mathbf{U}}^{\mathrm{ADV}}}
\newcommand{\V}{\mathbf{V}}
\newcommand{\dt}{\Delta t}
\newcommand{\dr}{\Delta r}

@@

\item {\bf React Base}$[(\rho h)_0^{\inp},(\overline{\rho\Hnuc})^{\inp},(\overline{\rho\Hext})^{\inp}] \rightarrow [(\rho h)_0^{\outp}]$\\
is the process by which we update the base state enthalpy through $\dt/2$ in time using
\begin{equation}
\frac{\partial(\rho h)_0}{\partial t} = (\overline{\rho\Hnuc})^{\inp} + (\overline{\rho\Hext})^{\inp}\enskip ,
\end{equation}
discretized as
\begin{equation}
(\rho h)_{0,j}^{\outp} = (\rho h)_{0,j}^{\inp} + \frac{\dt}{2}(\overline{\rho\Hnuc})_{j}^{\inp} + \frac{\dt}{2}(\overline{\rho\Hext})_{j}^{\inp} \enskip .
\end{equation}

@@

%--------------------------------------------------------------------------
% STEP 3
%--------------------------------------------------------------------------
\item[Step 3.] {\em React the full state and base state through the first time 
interval of $\dt / 2.$}

\item {\bf React State}$[\rho^n, (\rho h)^n, X_k^n, T^n, (\rho\Hext)^n]
                   \rightarrow$ $[ \rho^{(1)}, (\rho h)^{(1)}, X_k^{(1)}, T^{(1)},
                                  (\rho \omegadot_k)^{(1)}, (\rho \Hnuc)^{(1)} ].$

\item {\bf React Base}$[(\rho h)_0^n,(\overline{\rho \Hnuc})^{(1)},(\overline{\rho\Hext})^n] \rightarrow [(\rho h)_0^{(1)}]$

@@

\item {\bf React State}$[ \rho^{(2),\star},(\rho h)^{(2),\star}, X_k^{(2),\star}, 
                             T^{(2),\star}, (\rho\Hext)^{(2),\star}] $\\
$\rightarrow [ \rho^{n+1,\star},(\rho h)^{n+1,\star}, X_k^{n+1,\star}, T^{n+1,\star}, 
              (\rho \omegadot_k)^{(2),\star}, (\rho \Hnuc)^{(2),\star} ].$

@@

\item Update the species.  Here we do a difference approximation to
  eq.~\ref{eq:species}, neglecting the reaction terms.  The
  update consists of two steps:

@@

%--------------------------------------------------------------------------
% STEP 9
%--------------------------------------------------------------------------
\item[Step 9.] {\em React the full state and base state through a second time 
interval of $\dt / 2.$}

@@

\item {\bf React Base}$[(\rho h)_0^{(2)},(\overline{\rho \Hnuc})^{(2)},(\overline{\rho\Hext})^{(2)}] \rightarrow [(\rho h)_0^{n+1}]$
